The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-06 paper_draft.Rmd
adding the lny variable that works

#creating a table dividing the characteristics by urban/rural area
```
#Empirical Model

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         income2 = case_when(income == 0.0000 ~ 1.0000), 
         lny = log(income2))

reg_data %>%
  group_by(rural) %>%
  summarise(n = n())

>>>>

#creating a table dividing the characteristics by urban/rural area
```
#Empirical Model
see the link for math equation help.

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         lny = log(income + 1),
         valley = case_when(dept == "Chuquisaca", "Cochabamba", "Tarija" ~ 1,
                            dept != "Chuquisaca", "Cochabamba", "Tarija" ~ 0))

#adding the region variables for the region fixed-effects option

reg_data %>%
  group_by(dept_factor) %>%
  summarise(n = n())
